\section{Conclusions and outlook}

This paper proposed a stochastic Galerkin shallow flow model using the surface gradient method to ensure well-balancing.
The well-balancedness of the stochastic model was studied theoretically \rev{and verified in a series of idealised numerical tests, with a prescribed uncertainty that characterises topographic or bathymetric measurement errors.}
\rev{These tests demonstrated that the stochastic Galerkin model preserves well-balancing to machine precision, and accurately simulates steady flow over highly irregular and uncertain topography.}
\rev{Despite its relatively low-order Wiener-Hermite basis, the stochastic Galerkin model was able to simulate strongly nonlinear behaviour, producing discontinuous and highly non-Gaussian probability distributions that compared favourably against a Monte Carlo reference solution.}

It is likely that a more sophisticated treatment using a multiresolution wavelet decomposition \citep{lemaitre2004a,pettersson2014} or multi-element discretisation of the stochastic dimension \citep{wan-karniadakis2006,li-stinis2015} would further improve the representation of highly non-Gaussian and discontinuous probability distributions.
It is also likely that a decomposition or discretisation of stochastic space would simplify a stochastic reformulation of positivity preserving schemes involving nonlinear operators, so enabling the development of stochastic wetting-and-drying processes \rev{that are essential for flood inundation modelling}.
Such improvements are the subject of future work.

\rev{The one-dimensional stochastic Galerkin model presented here is ideally suited to river routing applications:
using as few as two expansion coefficients per element, the stochastic model can account for river bed measurement errors to produce a probabilistic simulation of the transient flow that is accurate and computationally efficient.}
Without parallelisation, the stochastic Galerkin model is \rev{at least} 100 times faster than a Monte Carlo simulation.
With parallelisation on commodity hardware, the computation time for the stochastic Galerkin model would be on par with a single iteration of the deterministic solver.

%The first test verified that a lake-at-rest over an uncertain bed was preserved to machine precision.
%The second test challenged the stochastic Galerkin model using steady-state critical flow over an uncertain bed.
%The test was designed to provoke strongly nonlinear behaviour such that about 50\% of flows were subcritical and the other 50\% develop a transcritical shock.
%The resulting probability distributions were discontinuous and highly non-Gaussian.
%\rev{A third test verified that the stochastic Galerkin model accurately simulates steady flow over a highly irregular and uncertain bed profile.}



